% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass[a4paper]{../res} 
\include{../preambleResume}
\textwidth=6.5in
%\addtolength{\textheight}{-3cm}

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\vspace{1\baselineskip}

% Date
8 November 2013

% Inside address
Anna Cooke \\
Student Recruitment Manager \\
PwC UK, Consulting \\
1 Hays Lane \\
London SE1 2RD

% Opening
Dear Ms. Cooke,

\textbf{Re: Associate Strategy Consultant via Oxford recruiting, London Office}

I've met with PwC at the Oxford Consultancy Fair, dined with PwC to get a broader understanding of the firm, and taken on a team-based Oxford Student Consultancy project. I'm committed to beginning my career in consulting and think that PwC would be a great place to start. 

As a final year DPhil in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills. My thesis entails computational modelling of DNA and single-molecule fluorescence studies of a DNA helicase implicated in rare childhood genetic disorders that greatly increase cancer risk. My undergraduate degree is in Biomedical Engineering and Economics from a leading US biomedical research institution, Johns Hopkins University. The aim is not to abandon my training; rather, to gain a broader perspective and ultimately command considerably more leverage, as a consultant, than I ever could in the lab.

Given my background and interest, the strongest fit is with strategy consulting, specifically the UK group of the global pharmaceuticals and life sciences practice. To confirm this suspicion, I reached out to a PhD scientist that has successfully navigated the transition from lab to consulting, Dr. Neil Deacon, an associate with the practice. He impressed upon me how potent the analytical and problem solving expertise of a doctorate can be when applied through the lens of business, a path I hope to follow. 


%The life sciences practice would be a strong fit, given my life sciences background. While I intend to gain exposure to a diverse array of industries in the first few years; in the longer-term, I would value working with a practice that fully utilizes my doctorate and technical background, including:
%\begin{itemize}[itemindent=1cm]
%    \item Extensive knowledge of DNA and protein structure
%    \item Programming and analytical ability to test my hypothesise on real data
%    \item Experience with devices and instrumentation
%    \item Practical experience with doctors and patients through work and volunteering in hospital 
%\end{itemize}
%Why would I disregard these valuable experiences to fit into a consultancy that doesn't value life sciences sector expertise or the value-added of a doctorate. A compelling argument, and one of the reasons I'm so drawn to PwC.

%One illustrative example of client/stakeholder management in a high-stakes environment is my work as a legislative aide to a Maryland State Legislature delegate, representing 100k constituents. I continued work on his anti-smoking legislation and coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. I was exposed to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. More importantly, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices.

Understandably, one may wonder what, other than raw analytical horsepower, a freshly minted DPhil can bring to the firm. Impact is the currency of a consultancy; PwC is worthless if it does not deliver value through actionable advice to clients. Segue to story\ldots legislative aide to a Maryland State Legislature delegate representing 100k constituents; 90 days to run the affairs of a state numbering 6 million; 4 person legislative office where I'm the only full-time legislative staffer. I reworked the logistics backend to deliver mailed session status reports to 6k people. I shepherded 3 bills from conception to passage, all of which play their small part in keeping Maryland healthy. I coordinated with stakeholders to the Insurance and Health Disparities subcommittees, navigating the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. None of this would have been possible without teamwork, effective communication and wholehearted dedication to the client, in this case the delegate and his constituents. More important than any individual outcome, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices.

For PwC, my value added is the ability to reduce ideas to practice, both through hardball analysis and the softer touch of stakeholder engagement. I'm excited by the prospect of working from a home base in the strategy consulting life science practice, a specialism where my background can best be brought to bear on client's toughest challenges. In the mid-term, in the interest of avoiding complete myopia, I look forward to staffing on some projects in high-demand areas outside of life sciences -- who knows, Risk with Barclays' treasury could make for a fun change of scenery.

In any case, thank you for your time and look forward to chatting soon.

% Closing
Sincerely, \\
Ryan M Harrison \\
PS. Work authorization: US (indefinite), UK (Aug-2015 via Tier 4 Doctorate Extension Scheme). 


\end{resume} 
\end{sloppypar}
\end{document} 



