% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 
\include{../preambleResume}
\textwidth=6.5in
%\addtolength{\textheight}{-3cm}

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\vspace{1\baselineskip}

% Date
28 October 2013
\vspace{1\baselineskip}

% Inside address
Human Resources \\
IMS Consulting Group \\
210 Pentonville Road \\
London N1 9JY
\vspace{1\baselineskip}

% Opening
%Dear Ms. Warin,
IMS Consulting Group:

\textbf{Re: Associate Consultant via Oxford recruiting. Offices: London, Cambridge}

% Write the body of the letter
I'm familiar with IMS Consulting Group through applying for a summer internship last year. Your 2012 case-based information session was valuable, and as a life sciences DPhil the firm is a natural fit. 

This year, I noticed your Associate Consulting posting (ref: 40779) on Oxford Career Services, dug-out my notes from last year, and meet with IMSCG at the Oxford Consultancy fair on 23 Oct. The fit hasn't changed -- given my combination of hands-on wetlab experience, health policy exposure and business interest in the life sciences ecosystem -- I'd make a strong addition to the firm.

My interest at the intersection of business and healthcare is not new. On the business and economics side, I've completed course work in econometrics, business strategy and corporate finance. This includes a study abroad in Denmark and undergraduate capstone project applying my knowledge to ascertaining the appropriateness of different GDP measures. 

As for healthcare, I found it most promising to pursue my interest outside the classroom, taking the opportunity to intern for both the Baltimore City Health Department and a delegate to the Maryland General Assembly on the Insurance and Health Disparities subcommittees. At the health department, I served as an analyst for the city's 2008 health status report and helped establish a baseline metric for flu reporting. In the state legislature, I was exposed to the complexities legislation, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. I coordinated with these stakeholders to amend legislation, and more importantly digest and communicate a variety of technical complexities to the delegate.

Education-wise, I'm finishing up a DPhil in Biophysics at the University of Oxford. My thesis entails computational modeling of DNA and single-molecule fluorescence studies of a DNA helicase implicated in rare childhood genetic disorders that greatly increase cancer risk. My undergraduate degree is in Biomedical Engineering and Economics from a leading US biomedical research institution, Johns Hopkins University.

For IMSCG, my value added lies in my ability to reduce ideas to practice, through either data analysis or coordination with key stakeholders. Thanks you for your time; look forward to hearing from you.


\vspace{1\baselineskip}
% Closing
Sincerely, \\
Ryan M Harrison \\

PS. I have work authorization in the US (indefinite) and UK (Aug-2015 via Tier 4 Doctorate Extension Scheme). 


\end{resume} 
\end{sloppypar}
\end{document} 



