% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass[a4paper]{../res} 

\include{../preambleResume}
\textwidth=6.5in

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
9 November 2013

% Inside address
Gemma Porter \\
Graduate Recruitment Manager \\
Oliver Wyman \\
55 Baker Street \\
London W1U 8EW
%\vspace{1\baselineskip}

% Opening
Dear Ms. Porter, % HR contact from 2013 Management consultancy book

\textbf{Re: London - Entry Level Consultant - Core Consultant Group - via Oxford Recruiting}

% Write the body of the letter
As a final year DPhil in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills. The aim is not to abandon my training; rather, to gain a broader perspective and ultimately command considerably more leverage, as a consultant, than I ever could as ``Just A Programmer.'' 

Over the years, I've met with Oliver Wyman at the Oxford Consultancy Fairs, spoken to Oliver Wyman consultants at your dedicated careers events and taken on a team-based Oxford Student Consultancy project. I'm committed to beginning my career in consulting and think that Oliver Wyman would be a fit.

The transition to consulting will require dedication and sacrifice -- tolls I have borne for causes I believe in, be it a water project in the Guatemalan highlands or persevering to complete a doctorate. Tolls I am more than happy to pay to build business acumen in the best training environment available. Eminently quotable parters also don't hurt -- I jest, but when Richard Balaban said, ``We do the \emph{I} word; we create impact,'' or spoke on training being in the ``enlightened self-interest'' of the firm, I believed him.

To prepare myself, I've reached out to PhD scientists that have successfully made the transition; for example, Dr. Nick Faull, a fellow Oxford physicist turned Engagement Manager with the financial services practice. He impressed upon me how potent the analytical and problem solving expertise of a doctorate can be when applied through the lens of business, a path I hope to follow. Training at the fringes of human knowledge instills a healthy respect for the limits of what we `know' and an ability to, in Dr. Faull's words, ``Challenge the conventional wisdom.''

%Although we met socially through mutual-friends, he was happy to take time from his busy schedule to chat, and has insisted on remaining in contact. 
%Understandably, one may wonder what, other than raw analytical horsepower, a freshly minted DPhil can bring to the firm. 
%This simple proposition is the bedrock of the firm and must flow from every consultant, regardless of how junior. 
Impact is the currency of a consultancy; Oliver Wyman is worthless if it does not deliver value through actionable advice to clients. Segue to story\ldots legislative aide to a Maryland State Legislature delegate representing 100k constituents; 90 days to run the affairs of a state numbering 6 million; 4 person legislative office where I'm the only full-time legislative staffer. I reworked the logistics backend to deliver mailed session status reports to 6k people. I shepherded 3 bills from conception to passage, all of which play their small part in keeping Maryland healthy. I coordinated with stakeholders to the Insurance and Health Disparities subcommittees, navigating the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. None of this would have been possible without teamwork, effective communication and wholehearted dedication to the client, in this case the delegate and his constituents. More important than any individual outcome, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices.


%Fairly or unfairly, DPhil applicants can be stereotyped as lacking in client management skills and knowledge of broader business ecosystems. To allay these concerns, I've worked to develop these skills outside of the research environment. 


%On the ecosystem side, I built foundational knowledge through coursework in econometrics, business strategy and corporate finance. This includes a business-focused study abroad in Denmark to better understand the Nordic model, an undergraduate capstone project ascertaining the appropriateness of different GDP measures and a science commercialization course at the Sa\"\i d Business School. To gain exposure to biotech in particular, I took the initiative and volunteered at exclusive industry conferences.

%As I've worked mostly with small research teams and start-ups, I've used this summer as an opportunity to learn more about the types of problems facing larger tech-focused firms, eventually landing in a R\&D role with NaturalMotion, a mid-sized games, animation and AI technology firm. The goal for this summer is to compare/contrast the small-scale environs I'm accustomed to, with the additional complications of running a larger firm. For example, the company is scaling very quickly and is increasingly struggling to maintain its culture; a problem class that I suspect faces many McKinsey clients after rapid organic growth or a large acquisition.

%\begin{description}[labelindent=1cm]
%    \item[Analytical] Handling scientific datasets from molecular simulation and image processing.
%\end{description}

For Oliver Wyman, my value added is the ability to reduce ideas to practice, both through hardball analysis and the softer touch of stakeholder engagement. In the mid-term, I'm excited by the prospect of working with a diverse array of clients. In the long-term, I look forward to specializing where my technical background can be brought to bare on client's toughest challenges, for example with the Health \& Life Sciences practice.

%Thank you for your time and consideration; I look forward to hearing from you.

%\vspace{1\baselineskip}
% Closing
Sincerely, \\
Ryan M Harrison

%DPhil Student in Computational Biophysics, University of Oxford \\ 
PS. Work authorization: US (indefinite), UK (Aug 2015, Tier 4 Doctorate Extension Scheme).
%PS. Work authorization in the US and UK (Tier 4 Doctorate Extension Scheme).

\end{resume} 
\end{sloppypar}
\end{document} 



