% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass[a4paper]{../res} 

\include{../preambleResume}
\textwidth=6.5in

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
4 November 2013

% Inside address
Scott Foster \\
Applied Predictive Technologies \\
Berkeley Square House \\
2nd Floor, Berkeley Square \\
London W1J 6BD
%\vspace{1\baselineskip}

% Opening
Dear Mr. Foster, % HR contact from 2013 Management consultancy book

\textbf{Re: Business Consultant via Oxford recruiting, London Office}

% Write the body of the letter
As a final year DPhil in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills. The aim is not to abandon my training; rather, to gain a broader perspective and ultimately command considerably more leverage as a consultant, than I ever could as ``Just A Programmer.'' Don't misunderstand, I love to code; however, in the analytics space, software is only as good as the results it helps people deliver. The transition from scientist to consultant will require dedication -- the same dedication I have applied to other causes I believe in, be it a water project in the Guatemalan highlands or completing a doctorate. 

I've met with APT at the Oxford Consultancy Fairs, taken on a team-based Oxford Student Consultancy project and reached out to PhD scientists that have successfully made the transition. It has been impressed upon me how potent the analytical and problem solving expertise of a doctorate can be when applied through the lens of business, a path I hope to follow. I'm committed to beginning my career in consulting and think the combination of business interest and technical background make me a great candidate for APT. 

%Although we met socially through mutual-friends, he was happy to take time from his busy schedule to chat, and has insisted on remaining in contact. 
%Understandably, one may wonder what, other than raw analytical horsepower, a freshly minted DPhil can bring to the firm. 
%This simple proposition is the bedrock of the firm and must flow from every consultant, regardless of how junior. 


%As I've worked mostly with small research teams and start-ups, I took a leave from my degree during summer 2013 to learn more about the problems facing larger tech-focused firms, eventually landing in a R\&D role with NaturalMotion, a mid-sized games, animation and AI technology firm. The goal for this summer is to compare/contrast the small-scale environs I'm accustomed to, with the additional complications of running a larger firm. I also gained experienced working in a corporate Agile environment, with a Microsoft toolchain, on a large codebase. In otherwords, I'm familiar with the differences between academic and commercial quality code.

Despite APTs history of success, the firm is worthless if it does not deliver value through actionable advice to clients. Always happy to discuss code refactoring, testing methodologies and the differences between academic/commercial code; however, I think a non-tech story is more instructive. A long time ago in a galaxy far, far away I served as a legislative aide to a Maryland State Legislature delegate representing 100k constituents. 90 days to run the affairs of a state numbering 6 million. 4 person legislative office where I'm the only legislative full-timer.

I reworked the logistics backend to deliver mailed session status reports to 6k people. I shepherded 3 bills from conception to passage, all of which play their small part in keeping Maryland healthy. I coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. I was exposed to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. None of this would have been possible without teamwork, effective communication and wholehearted dedication to the client, in this case the delegate and his constituents. More important than any individual outcome, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices.


%Fairly or unfairly, DPhil applicants can be stereotyped as lacking in client management skills and knowledge of broader business ecosystems. To allay these concerns, I've worked to develop these skills outside of the research environment. 


%On the ecosystem side, I built foundational knowledge through coursework in econometrics, business strategy and corporate finance. This includes a business-focused study abroad in Denmark to better understand the Nordic model, an undergraduate capstone project ascertaining the appropriateness of different GDP measures and a science commercialization course at the Sa\"\i d Business School. To gain exposure to biotech in particular, I took the initiative and volunteered at exclusive industry conferences.

%As I've worked mostly with small research teams and start-ups, I've used this summer as an opportunity to learn more about the types of problems facing larger tech-focused firms, eventually landing in a R\&D role with NaturalMotion, a mid-sized games, animation and AI technology firm. The goal for this summer is to compare/contrast the small-scale environs I'm accustomed to, with the additional complications of running a larger firm. For example, the company is scaling very quickly and is increasingly struggling to maintain its culture; a problem class that I suspect faces many McKinsey clients after rapid organic growth or a large acquisition.

%\begin{description}[labelindent=1cm]
%    \item[Analytical] Handling scientific datasets from molecular simulation and image processing.
%\end{description}

For APT, my value added is the ability to reduce ideas to practice, through both data analysis and coordination with key stakeholders. It's the combination of tech and the softer skills that underscore my personal value add. Thank you for your time and consideration; I look forward to a mutually beneficial nerd-out. 


%\vspace{1\baselineskip}
% Closing
Sincerely,
\\ \\ \\ \\
Ryan M Harrison \\ \\
%DPhil Student in Computational Biophysics, University of Oxford \\ 
PS. Work authorization: US (indefinite), UK (Aug 2015, Tier 4 Doctorate Extension Scheme).
%PS. Work authorization in the US and UK (Tier 4 Doctorate Extension Scheme).

\end{resume} 
\end{sloppypar}
\end{document} 



