% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\addtolength{\textheight}{3cm}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage[osf]{mathpazo}
%\renewcommand*\familydefault{\ttdefault}
%\renewcommand*\familydefault{\sfdefault} 

\usepackage{microtype}
\usepackage[english]{babel}


% List and enumeration
%\usepackage{enumitem}
%\setitemize{itemsep=1pt,topsep=1pt,parsep=1pt,partopsep=1pt}


\begin{document} 
\begin{sloppypar}
 
\name{\textbf{\textsf{Ryan M Harrison}}\\ \\} % the \\[12pt] adds a blank line after name
 
% res package only supports two resumes -- Updated it to support three.

\address{2115 Cloville Avenue\\
         Baltimore, MD 21214\\
         \texttt{+}1 443 257 5953}
\address{\texttt{ryan.m.harrison@gmail.com}\\
         \texttt{linkedin.com/in/rmharri}\\
         \texttt{github.com/rmharrison}}
\address{Wolfson College\\ 
         Oxford OX2 6UD\\
         \texttt{+}44 07523 229446}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
\vspace{2\baselineskip}

% Date
19 October 2013
\vspace{1\baselineskip}

% Inside address
Atos Consulting Limited \\
4 Triton Square \\
Regent's Place \\
London \\
NW1 3HG
\vspace{1\baselineskip}

% Opening
Atos UK Recruiting:

\textbf{Re: Junior Business Technology Strategy Consultant}

% Write the body of the letter
I'm a final year DPhil student at the University of Oxford interested in a junior Business Technology Consultant role. Developing the domain specific knowledge to deeply understand the tech-aspects of a client case is appealing to me. My aim isn't to abandon my technical training, rather to gain a broader perspective, master my domain, and ultimately command considerably more leverage than I could ever hope to as a programmer. 

I'm no stranger to technology-oriented firms, having previously interned at two start-ups, a next gen sequencing company and a synthetic biology shop. As a programmer with significant wet lab experience, I was able to directly communicate with both software developers and biologist, two groups who can often misunderstand each other. 

As I've worked mostly with small research teams and start-ups, I took a leave from my degree during summer 2013 to learn more about the problems facing larger tech-focused firms, eventually landing in a R\&D role with NaturalMotion, a mid-sized games, animation and AI technology firm. The goal for this summer is to compare/contrast the small-scale environs I'm accustomed to, with the additional complications of running a larger firm. I also gained experienced working in a corporate Agile environment, with a Microsoft toolchain, on a large codebase.

On the business side, I took the initiative and volunteered at several exclusive industry conferences. I've also supplemented my undergraduate economics coursework with an international business study abroad focused on the Nordic model. More recently, I've taken the opportunity to learn more about UK science commercialization through a course offered by the Sa\"\i d Business School. From these academic and practical experiences, I've gained a working knowledge of economics, corporate finance and basic business strategy.

I hope to combine my tech acumen and demonstrated interest in business as a technology consultant with Atos. Thank you for taking the time to review my application.

\vspace{1\baselineskip}
% Closing
Sincerely,
\vspace{2\baselineskip}

Ryan M Harrison \\
DPhil Student \\
Computational Biophysics\\
University of Oxford \\


\end{resume} 
\end{sloppypar}
\end{document} 



