% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\include{../preambleResume}
\textwidth=6.5in

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
\vspace{1\baselineskip}

% Date
26 October 2013
\vspace{1\baselineskip}

% Inside address
Booz \& Co \\
7 Savoy Court \\
Strand \\
London WC2R 0JP
\vspace{1\baselineskip}

% Opening
Ms. Payal Khakhria: % HR contact from 2013 Management consultancy book

\textbf{Re: Senior Consultant (Oxford), London}

% Write the body of the letter
As a final year DPhil in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills. The aim is not to abandon my training; rather, to gain a broader perspective and ultimately command considerably more leverage as a consultant, than I ever could as ``Just A Programmer.''

I've met with Booz at the Oxford career fairs, spoken to Booz consultants at your networking events, taken on a team-based Oxford Student Consultancy project and reached out to PhD scientists that have successfully made the transition. I'm committed to beginning my career in consulting and think that Booz would be a great place to start.

Booz doesn't stop with blue book recommendations, but continues working with clients on the initial stages of reducing strategic objectives to practice. I think Mr. Clark, the parter who lead up the Oxford presentation, called it ``Pragmatic Strategy.'' Whatever it's called, my engineer's heart enjoys quickly becoming a wonk on client problems and distilling that knowledge base into implementable solutions. I also enjoyed speaking with Dr. Chan-Cheong Siew about his growth from PhD to Sr. Associate. He's an example of how potent the analytical and problem solving expertise of a doctorate can be when applied through the lens of business, a path I hope to follow.

Understandably, one may wonder what, other than raw analytical horsepower, a freshly minted DPhil can bring to the firm. One illustrative example of client/stakeholder management in a high-stakes environment is my work as a legislative aide to a Maryland State Legislature delegate, representing 100k constituents. I continued work on his anti-smoking legislation and coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. I was exposed to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. More importantly, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices.


%Fairly or unfairly, DPhil applicants can be stereotyped as lacking in client management skills and knowledge of broader business ecosystems. To allay these concerns, I've worked to develop these skills outside of the research environment. 


%On the ecosystem side, I built foundational knowledge through coursework in econometrics, business strategy and corporate finance. This includes a business-focused study abroad in Denmark to better understand the Nordic model, an undergraduate capstone project ascertaining the appropriateness of different GDP measures and a science commercialization course at the Sa\"\i d Business School. To gain exposure to biotech in particular, I took the initiative and volunteered at exclusive industry conferences.

%As I've worked mostly with small research teams and start-ups, I've used this summer as an opportunity to learn more about the types of problems facing larger tech-focused firms, eventually landing in a R\&D role with NaturalMotion, a mid-sized games, animation and AI technology firm. The goal for this summer is to compare/contrast the small-scale environs I'm accustomed to, with the additional complications of running a larger firm. For example, the company is scaling very quickly and is increasingly struggling to maintain its culture; a problem class that I suspect faces many McKinsey clients after rapid organic growth or a large acquisition.

%\begin{description}[labelindent=1cm]
%    \item[Analytical] Handling scientific datasets from molecular simulation and image processing.
%\end{description}

For Booz, my value added is the ability to reduce ideas to practice, through both data analysis and coordination with key stakeholders. In the mid-term, I'm excited by the prospect of working with a diverse array of clients. In the long-term, I look forward to specializing where my technical background can be brought to bare on client's toughest challenges, for example with DBT (Digital Business \& Technology).

\vspace{1\baselineskip}
% Closing
Sincerely,
\\
Ryan M Harrison \\ \\ \\
%DPhil Student in Computational Biophysics, University of Oxford \\ 
PS. Work authorization: US (indefinite), UK (Aug 2015, Tier 4 Doctorate Extension Scheme).
%PS. Work authorization in the US and UK (Tier 4 Doctorate Extension Scheme).

\end{resume} 
\end{sloppypar}
\end{document} 



