% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\include{../preambleResume}
\textwidth=6.5in

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
30 October 2013

% Inside address
Danielle Lestrade, Recruitment Officer \\
OC\&C Strategy Consultants \\
6 New Street Square \\
London EC4A 3AT

% Opening
Dear Ms. Lestrade, % HR contact from 2013 Management consultancy book

\textbf{Re: Associate Consultant via Oxford recruiting, London Office}

% Write the body of the letter
As a final year DPhil in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills. The aim is not to abandon my training; rather, to gain a broader perspective and ultimately command considerably more leverage as a consultant, than I ever could as ``Just A Programmer.'' 

Over the years, I've met with OC\&C at the Oxford Consultancy Fairs, spoken to OC\&C consultants at your networking events, taken on a team-based Oxford Student Consultancy project and reached out to PhD scientists that have successfully made the transition; for example, Dr. Tom Gladstone, a London partner who impressed upon me how potent the analytical and problem solving expertise of a doctorate can be when applied through the lens of business, a path I hope to follow. I'm committed to beginning my career in consulting and think that OC\&C would be a great place to start.

The transformation will require dedication and sacrifice -- tolls I have borne for causes I believe in, be it a water project in the Guatemalan highlands or persevering to complete a doctorate. Tolls I am more than happy to pay to build business acumen in the best training environment available. Outside of your partner's eminent quotability -- I jest, but when a certain founding member said, ``The \emph{best} training path you can possibly follow,'' I believed him -- the firm's biggest draws are its independence and demonstrated commitment to keeping consulting at a human-scale, which is reflected in your recruiting. Furthermore, I was genuinely impressed by the no BS sincerity of your consultants. 

Given industry consolidation -- R.I.P. Booz -- OC\&C is acutely aware that it will die unless it delivers value through actionable advice to clients. One illustrative example of client impact in a high-stakes environment is my work as a legislative aide to a Maryland State Legislature delegate representing 100k constituents. 90 days to run the affairs of a state numbering 6 million. 4 person office where I'm the only legislative full-timer.

I reworked the logistics backend to deliver mailed session status reports to 6k people. I shepherded 3 bills from conception to passage, all of which play their small part in keeping Maryland healthy. I coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. I was exposed to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. None of this would have been possible without teamwork, effective communication and wholehearted dedication to the client, in this case the delegate and his constituents. More important than any individual outcome, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices.

For OC\&C, my value is the ability to reduce ideas to practice, through both data analysis and coordination with key stakeholders. Thank you for your time and consideration; I look forward to hearing from you.

% Closing
Sincerely,
\\
Ryan M Harrison \\
%DPhil Student in Computational Biophysics, University of Oxford \\ 
PS. Work authorization: US (indefinite), UK (Aug 2015, Tier 4 Doctorate Extension Scheme).
%PS. Work authorization in the US and UK (Tier 4 Doctorate Extension Scheme).

\end{resume} 
\end{sloppypar}
\end{document} 



