% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\include{../preambleResume}
\textwidth=6.5in
\addtolength{\textheight}{-3cm}

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
%\vspace{1\baselineskip}
26 April 2014

% Inside address
Dr. Chris Von Seggern \\
ClearView Healthcare Partners \\
One Newton Place \\
275 Washington Street, Suite 405 \\
Newton, MA 02458
%\vspace{1\baselineskip}

% Opening
Dr. Von Seggern:

\textbf{Re: Connect To ClearView}

% Write the body of the letter
Please consider me for a place in the 2014 Connect To ClearView programme. I'm an ideal fit for ClearView and would welcome the opportunity to reconnect with the firm.

I've been interested in ClearView since its foundation and had the pleasure of interviewing with the firm in early 2009, after completing a degree in Biomedical Engineering from Johns Hopkins University. In speaking with analysts Patrick Dospoy (now finishing up a PhD himself), Katie Crawford and parter Dr. Chao, I discovered a firm in which I could flourish. Despite Dr. Chao taking the time to personally reassure me with vote-of-confidence, I withdrew my application precisely because I lacked confidence.

Five years later, I'm now finishing up a DPhil (PhD) in Biophysics from the University of Oxford, through the support of NSF and NIH fellowships. My interest in life sciences consulting has emerged stronger, supported by the expertise and grit a doctorate endears. More importantly, through work experience, both technical and non-technical, I have built confidence and abilities that I lacked as a fresh Uni grad. 

I will be relocating to Boston this August, and believe that ClearView is an even better fit now, than it was those many years ago. To confirm this suspicion, I reached out to Dr. Stephen Chapin, who not too long ago made the transition from PhD to consulting himself. The commitment to people, enduring client relationships and genial culture have not changed, despite the firms growth from a regional niche player to a boutique supporting multiple national and international projects, all together punching far above its apparent weight. 

I would like to use the Connect To ClearView programme as an opportunity to reconnect with the firm, and broader life sciences consulting ecosystem in Boston. Further, I suspect that ClearView would use the programme as an opportunity for an extended interview, to probe my growth as a candidate over the intervening years. As such, I have also submitted an off-cycle full-time consultant application.

In closing, my value to ClearView can be summarized in terms of two core competencies: 
%\begin{itemize}[itemindent=1cm]
\begin{itemize}
    \item A demonstrated interest in business, backed by training (e.g. economics, econometrics and corporate strategy) and exposure (e.g. volunteering at VC \& biotech conferences).
    \item A broad understanding of the life sciences ecosystem, including competence in both software and wetlab.
\end{itemize}
Both of these core competencies are backed by practical experience as well as theory. Thank you for your time and consideration. I hope to meet you in Boston this August.

% Closing
Sincerely, \\
Ryan M Harrison, DPhil Candidate \\
Computational Biophysics \\
University of Oxford  \\
Work authorization: US Citizen, UK Tier 4 Doctorate Extension Scheme (until Aug 2015)
\end{resume} 
\end{sloppypar}
\end{document} 



