% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass[a4paper]{../res} 

\include{../preambleResume}
\textwidth=6.5in

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
Human Resources \\
Code 01/14U \\
Department of Legislative Services \\
90 State Circle \\
Room 311 \\
Annapolis, MD \\
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
9 April 2014

% Inside address

%\vspace{1\baselineskip}

% Opening
\textbf{Re: Computer Programmers/Analysts (Code 01/14U)}

% Write the body of the letter
I understand that a PhD in Computational Biophysics from the University of Oxford isn't the usual starting point for a Maryland General Assembly analyst; however, I have served as a legislative aide with the Maryland General Assembly, have an active interest in policy, and have honed my programming, analytical and quantitative skills well beyond those of a typical computer science undergraduate. 

Don't let the Oxford branding fool you, I'm a Baltimore native and proud product of the Baltimore City School System. Currently completing a doctorate in Oxford under the aegis of the National Institutes of Health (NIH-Oxford Scholar) and National Science Foundation (Graduate Research Fellow). Prior to the PhD, I earned a degree in Biomedical Engineering from Johns Hopkins University.

I thought I'd take the opportunity share with you just one example of my personal impact. There are numerous technical examples, but I'm assuming that given my background, you'd be more interested in the non-technical, my time serving as a legislative aide to a Maryland State General Assembly, in the office of a Baltimore City delegate. You know the drill: 90 days to run the affairs of a state numbering 6 million in an understaffed legislative office where the secretary and I are the only full-timers.

I reworked the logistics backend to deliver mailed session status reports to 6k people, shepherded 3 bills from conception to passage and coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. The process exposed me to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. None of this would have been possible without teamwork, effective communication and wholehearted dedication to the client, in this case the delegate and his constituents. More important than any individual outcome, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices. I suspect these are the types of `soft skills' I'd use every day as an analyst.

Briefly, on the technical side, amongst other projects, I have deployed Ruby on Rails and Django intranet web applications with complex custom back-ends for a small synthetic biology start-up. This computer aided design software allowed the company to scale its DNA assembly pipeline. The software included complete in-code documentation for both low-level functions and high-level usage, as well as a complete unit and integration test suite. My application development experience is not theoretical; it is grounded in implementation.


%Fairly or unfairly, DPhil applicants can be stereotyped as lacking in client management skills and knowledge of broader business ecosystems. To allay these concerns, I've worked to develop these skills outside of the research environment. 


%On the ecosystem side, I built foundational knowledge through coursework in econometrics, business strategy and corporate finance. This includes a business-focused study abroad in Denmark to better understand the Nordic model, an undergraduate capstone project ascertaining the appropriateness of different GDP measures and a science commercialization course at the Sa\"\i d Business School. To gain exposure to biotech in particular, I took the initiative and volunteered at exclusive industry conferences.

%As I've worked mostly with small research teams and start-ups, I've used this summer as an opportunity to learn more about the types of problems facing larger tech-focused firms, eventually landing in a R\&D role with NaturalMotion, a mid-sized games, animation and AI technology firm. The goal for this summer is to compare/contrast the small-scale environs I'm accustomed to, with the additional complications of running a larger firm. For example, the company is scaling very quickly and is increasingly struggling to maintain its culture; a problem class that I suspect faces many McKinsey clients after rapid organic growth or a large acquisition.

%\begin{description}[labelindent=1cm]
%    \item[Analytical] Handling scientific datasets from molecular simulation and image processing.
%\end{description}

%My value added is the ability to reduce ideas to practice, through both data analysis and coordination with key stakeholders. In the mid-term, I'm excited by the prospect of working with a diverse array of clients. In the long-term, I look forward to specializing where my technical background can be brought to bare on client's toughest challenges, for example with the Pharmaceuticals or Medical Technology practices.

A slightly unusual candidate, yes. The skills, experience, and interest to excel at the job, also yes. 

Thank you for your time and consideration; I look forward to hearing from you.

%\vspace{1\baselineskip}
% Closing
Sincerely,
\\
Ryan M Harrison \\
Doctoral Candidate in Computational Biophysics, University of Oxford \\  \\
PS. Work authorization: US (indefinite)
%PS. Work authorization in the US and UK (Tier 4 Doctorate Extension Scheme).

\end{resume} 
\end{sloppypar}
\end{document} 



