% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\include{../preambleResume}
\textwidth=6.5in
\textheight 11in %RMH
\addtolength{\textheight}{-3cm}

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
5 May 2014

% Inside address
Victor Velculescu, M.D. Ph.D., CSO \\
Personal Genome Diagnostics, Inc. \\
2809 Boston St, Suite 503 \\
Baltimore, MD 21224 \\
%\vspace{1\baselineskip}

% Opening
Dr. Velculescu:

\textbf{Re: Genomics Analyst / Associate Scientist}

% Write the body of the letter
When I learned about Personal Genome through Johns Hopkins University career services (ID: 60357), I was estatic. We're a great fit, and here's why\ldots

My value to Personal Genome stems from three core competencies: 
\begin{itemize}[itemindent=1cm]
    \item Collaborative software development experience supplemented with extensive simulation method and data processing experience
    \item Detailed molecular understanding of DNA, including a stint developing a pre-release next-generation sequencer
    \item A demonstrated interest in the life sciences ecosystem
\end{itemize}

These core competencies are backed by both a solid academic foundation and practical industry experience. I have served as a developer for two large-scale pieces of academic software, the Rosetta Protein Structure Prediction Suite and the oxDNA coarse-grained DNA model. I've also worked with 3 companies, one of which was Ion Torrent Systems, builders of the Personal Genome Machine. As such, I'm familiar with next-gen sequencing approaches, Ion in particular at a hardware and read-quality determination level. 

I'll be relocating back to the US in August 2014, after submitting my thesis. Currently finishing up a doctorate Computational Biophysics at the University of Oxford, under the aegis and generous fellowship support of the NSF and NIH. In fact, as an NIH graduate partnership student completing a portion of my dissertation work at the NIH, I was a contemporary of one of your current scientist, Dr. Sonya Parpart.

On a personal note, I'm a Baltimore native; proud product of Baltimore City Schools and Johns Hopkins University Whiting School of Engineering. Baltimore isn't exactly a life sciences hub, and I wasn't expecting to identify a firm with such a perfect fit outside of hubs like Boston. I'm glad I've been shown lacking, in my faith in the city's start-up landscape.

I would be very excited to further discuss my fit with the firm. Thank you for your time and attention. I look forward to hearing from you.

% Closing
Sincerely, \\
Ryan M Harrison \\ 
DPhil Candidate \\
Computational Biophysics \\
University of Oxford  \\
PS. Work authorization: US (indefinite), UK (Aug 2015, Tier 4 Doctorate Extension Scheme).
\end{resume} 
\end{sloppypar}
\end{document} 

%Note upon JHU submission (ID: 60357)
%Baltimore native and DNA extraordinary ecstatic to learn about your firm. Finishing up a doctorate in Computational Biophysics (molecular simulation of DNA) at the University of Oxford. Relocating back to the states in August 2014. Probably more suitable for an Associate Scientist position, but I just couldn't pass up the opportunity to potentially work with a Baltimore-based biotech start-up.

%Note that at Oxford, doctorates are called DPhils, and are entirely research based. No transcript.

%No surprise\ldotsINTP. Surprisingly well balanced between Math and Verbal on Standardized tests, e.g. 700/V and 670/M on SAT (back when it was out of 1600 total).
