% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\addtolength{\textheight}{3cm}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage[osf]{mathpazo}
%\renewcommand*\familydefault{\ttdefault}
%\renewcommand*\familydefault{\sfdefault} 

\usepackage{microtype}
\usepackage[english]{babel}


% List and enumeration
\usepackage{enumitem}
%\setdescription{leftmargin=\parindent,labelindent=\parindent}
%\setitemize{itemsep=1pt,topsep=1pt,parsep=1pt,partopsep=1pt}


\begin{document} 
\begin{sloppypar}
 
\name{\textbf{\textsf{Ryan M Harrison}}\\ \\} % the \\[12pt] adds a blank line after name
 
% res package only supports two resumes -- Updated it to support three.

%\address{2115 Cloville Avenue\\
%         Baltimore, MD 21214\\
%         \texttt{+}1 443 257 5953}
%\address{\texttt{ryan.m.harrison@gmail.com}\\
%         \texttt{linkedin.com/in/rmharri}\\
%         \texttt{github.com/rmharrison}}
%\address{Wolfson College\\ 
%         Oxford OX2 6UD\\
%         \texttt{+}44 07523 229446}

\address{2115 Cloville Avenue\\
         Baltimore, MD 21214\\
         +1 443 257 5953}
\address{ryan.m.harrison@gmail.com\\
         linkedin.com/in/rmharri\\
         github.com/rmharrison}
\address{Wolfson College\\ 
         Oxford OX2 6UD\\
         +44 (0) 7523 229446}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
\vspace{2\baselineskip}

% Date
19 October 2013
\vspace{1\baselineskip}

% Inside address
London Recruiting Team \\
Simon-Kucher \& Partners \\
3rd Floor, 1 Plough Place \\
Fetter Lane \\
London EC4A 1DE \\
%\vspace{1\baselineskip}

% Opening
%Mr. Mark Billige:
Dear Mr. Billige,

\textbf{Re: Graduate Consultant Position, London}

% Write the body of the letter
As a final year DPhil in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills. I've met with Simon-Kucher at the Oxford career fairs, taken on a team-based Oxford Student Consultancy project and reached out to PhD scientists that have successfully made the transition. Although I'm committed to beginning my career in consulting, one may understandably wonder what, other than raw analytical horsepower, a freshly minted DPhil student can bring to a firm like Simon-Kucher.

On the client management side, I served as a legislative aide in the Maryland House of Delegates, the lower house of the state legislature. The work allowed me to coordinate closely with stakeholders to the Insurance and Health Disparities subcommittees and exposed me to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. More importantly, I learned how to manage up, to best provide actionable material, as well as laterally, to coordinate with legislative staff in other offices. On the business knowledge side, I've built foundations through coursework in econometrics, business strategy and corporate finance. To gain additional exposure, I took the initiative and volunteered at the Mid-Atlantic Biotech and Venture Capital conferences.

As I've worked mostly with small research teams and start-ups, I took this summer as an opportunity to explore a larger firm through an R\&D internship with NaturalMotion, a mid-sized game and middleware company. Despite my role in R\&D, I was given wide latitude to explore the company. I found myself drawn to the analytics department, where they work on monetizing the company's free-to-play mobile games. These were people like me -- PhDs -- building economic models and tweaking in-game economies in real-time. Price discrimination and market segmentation built directly from player actions; tens of millions in revenue from micropayments for virtual cars. This is the beginnings of data driven pricing, and it's probably the future. 

For Simon-Kucher, my value added is the ability to reduce ideas to practice, through both data analysis and coordination with key stakeholders. Combining familiar technical skills, like regression and time-series analysis, with an active interest in economics, pricing analytics is an area where I can deliver real value to clients. I'm eager to learn more about the sales \& marketing side of operations, particularly in the biotech space. Thank you for your time and consideration; I look forward to hearing from you.

\vspace{1\baselineskip}
% Closing
Sincerely,
\vspace{2\baselineskip}

Ryan M Harrison \\ \\ \\
%DPhil Student in Computational Biophysics, University of Oxford \\ \\
%PS. Work authorization in the US and UK (Tier 4 Doctorate Extension Scheme).
PS. Work authorization in the US and UK.

\end{resume} 
\end{sloppypar}
\end{document} 



