% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\addtolength{\textheight}{3cm}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage[osf]{mathpazo}
%\renewcommand*\familydefault{\ttdefault}
%\renewcommand*\familydefault{\sfdefault} 

\usepackage{microtype}
\usepackage[english]{babel}


% List and enumeration
\usepackage{enumitem}
%\setdescription{leftmargin=\parindent,labelindent=\parindent}
%\setitemize{itemsep=1pt,topsep=1pt,parsep=1pt,partopsep=1pt}


\begin{document} 
\begin{sloppypar}
 
\include{includeHeader}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
\vspace{2\baselineskip}

% Date
19 October 2013
\vspace{1\baselineskip}

% Inside address
Kurt Salmon \\
10 Fleet Place \\
London EC4M 7RB
\vspace{1\baselineskip}

% Opening
Kurt Salmon UK HR Representative:

\textbf{Re: Graduate Consultant Position, London \& Manchester}

% Write the body of the letter
As a final year DPhil in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills. Fairly or unfairly, DPhil applicants can be stereotyped as lacking in client management skills and knowledge of broader business ecosystems. To allay these concerns, I've worked to develop these skills outside of the research environment. I've taken on a team-based Oxford Student Consultancy project, reached out to PhD scientists that have successfully made the transition and am committed to beginning my career as a consultant. 

%The aim is not to abandon my training; rather, to gain a broader perspective and ultimately command considerably more leverage as a consultant, than I ever could as ``Just A Programmer.''


%Understandably, one may wonder what, other than raw analytical horsepower, a freshly minted DPhil can bring to Kurt Salmon. 

On the client management side, I took the opportunity to intern with Baltimore City Health Department, where I worked on a youth anti-smoking campaign and served as an analyst for the City's annual heath status report. A delegate to the Maryland General Assembly, representing 100k constituents, saw the value in my technical training -- Biomedical Engineering and Economics at the undergraduate level -- and invited me to serve as a legislative aide. I continued work on his anti-smoking legislation and coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. I was exposed to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. More importantly, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices.

On the ecosystem side, I built foundational knowledge through coursework in econometrics, business strategy and corporate finance. This includes a business-focused study abroad in Denmark to better understand the Nordic model, an undergraduate capstone project ascertaining the appropriateness of different GDP measures and a science commercialization course at the Sa\"\i d Business School. To gain additional exposure, I took the initiative and volunteered at the Mid-Atlantic Biotech and Venture Capital conferences.

%As I've worked mostly with small research teams and start-ups, I've used this summer as an opportunity to learn more about the types of problems facing larger tech-focused firms, eventually landing in a R\&D role with NaturalMotion, a mid-sized games, animation and AI technology firm. The goal for this summer is to compare/contrast the small-scale environs I'm accustomed to, with the additional complications of running a larger firm. For example, the company is scaling very quickly and is increasingly struggling to maintain its culture; a problem class that I suspect faces many McKinsey clients after rapid organic growth or a large acquisition.

%\begin{description}[labelindent=1cm]
%    \item[Analytical] Handling scientific datasets from molecular simulation and image processing.
%\end{description}

For Kurt Salmon, my value added is the ability to reduce ideas to practice, through both data analysis and coordination with key stakeholders. Thank you for your time and consideration.



\vspace{1\baselineskip}
% Closing
Sincerely,
\vspace{2\baselineskip}

Ryan M Harrison \\ \\ \\
%DPhil Student in Computational Biophysics, University of Oxford \\ \\
%PS. Work authorization in the US and UK (Tier 4 Doctorate Extension Scheme).
PS. Work authorization in the US and UK.

\end{resume} 
\end{sloppypar}
\end{document} 



