% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\include{../preambleResume}
\textwidth=6.5in
\textheight 11in %RMH
\addtolength{\textheight}{-3cm}

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
%\vspace{1\baselineskip}
5 May 2014

% Inside address
Elizabeth Rountree \\
221 Main Street, Suite 1580 \\
San Francisco, CA 94105 \\
%\vspace{1\baselineskip}

% Opening
Mrs. Rountree: 

\textbf{Re: Biotech Analyst}

% Write the body of the letter
Please consider me as a candidate for an Analyst position. I'm an ideal fit for C1 and would welcome the opportunity to connect with the firm.

The decision to pursue a career in consulting has not been taken lightly. Over the years, I've taken extensive coursework on business, economics and strategy (feel free to quiz me), worked on a team-based Oxford Student Consultancy project and reached out to PhD scientists that have successfully made the transition. They impressed upon me how potent the analytical and problem solving expertise of a doctorate can be when applied through the lens of business, a path I hope to follow. I'm committed to beginning my career in consulting and think that a boutique like C1 would be a great fit.

I'm now finishing up a DPhil (PhD) in Biophysics from the University of Oxford, through the support of NSF and NIH fellowships. My interest in life sciences consulting has emerged stronger, supported by the expertise and grit a doctorate endears. More importantly, through work experience, both technical and non-technical, I have demonstrated value on a succession of projects, many of which are in the broader life sciences ecosystem.

I will be relocating back to the US in August 2014, after submitting my doctoral thesis. My preference would be for your Boston office, but I understand that client demand and company needs come first.

My value to C1 can be summarized in terms of two core competencies: 
%\begin{itemize}[itemindent=1cm]
\begin{itemize}
    \item A demonstrated interest in business, backed by training (e.g. economics, econometrics and corporate strategy) and exposure (e.g. volunteering at VC \& biotech conferences).
    \item A broad understanding of the life sciences ecosystem, including competence in both software and wetlab.
\end{itemize}
Both of these core competencies are backed by practical experience as well as theory. The core competencies are complemented by well honed quantitative training, including technical skills (e.g. programming, modelling and statistical analysis), wetlab skills (i.e. I am a competent molecular biologist, and enjoy speaking with bench scientist), and an interest in the non-technical aspects of the life sciences ecosystem (e.g. policy internships with a city health department and state health legislation).

I'd be thrilled to further discuss how my skillset and experience would be an asset to C1. Thank you for your time and consideration.

% Closing
Sincerely, \\
Ryan M Harrison, DPhil Candidate \\
Computational Biophysics \\
University of Oxford  \\
Work authorization: US Citizen, UK Tier 4 Doctorate Extension Scheme (until Aug 2015)
\end{resume} 
\end{sloppypar}
\end{document} 



