% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\addtolength{\textheight}{3cm}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
%\usepackage[osf]{mathpazo}
%\renewcommand*\familydefault{\ttdefault}
%\renewcommand*\familydefault{\sfdefault} 

\usepackage{microtype}
\usepackage[english]{babel}


% List and enumeration
%\usepackage{enumitem}
%\setitemize{itemsep=1pt,topsep=1pt,parsep=1pt,partopsep=1pt}


\begin{document} 
\begin{sloppypar}
 
\name{\textbf{\textsf{Ryan M Harrison}}\\ \\} % the \\[12pt] adds a blank line after name
 
% res package only supports two resumes -- Updated it to support three.

\address{2115 Cloville Avenue\\
         Baltimore, MD 21214\\
         \texttt{+}1 443 257 5953}
\address{\texttt{ryan.m.harrison@gmail.com}\\
         \texttt{linkedin.com/in/rmharri}\\
         \texttt{github.com/rmharrison}}
\address{Wolfson College\\ 
         Oxford OX2 6UD\\
         \texttt{+}44 07523 229446}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
\vspace{2\baselineskip}

% Date
17 October 2013
\vspace{1\baselineskip}

% Inside address
Human Resources \\
PRMA Consulting Ltd. \\
Cygnus House \\
1 Waterfront Business Park \\
Fleet, Hampshire \\
GU51 3QT
\vspace{1\baselineskip}

% Opening
%Dear Ms. Warin,
Ms. Sharon B.:

\textbf{Re: Analyst, Life Sciences}

% Write the body of the letter
I noticed your life sciences analyst posting on Oxford Career Services; given my combination of hands-on wetlab experience, programming knowledge and econometrics training, I thought I might be a good fit.

My interest in economics and healthcare is not new. I've completed course work in econometrics, business strategy and corporate finance. This includes a study abroad in Denmark and undergraduate capstone project applying my knowledge to ascertaining the appropriateness of different GDP measures. 

As for healthcare, I found it most promising to pursue my interest outside the classroom, taking the opportunity to intern for both the Baltimore City Health Department and a delegate to the Maryland General Assembly on the Insurance and Health Disparities subcommittees. At the health department, I served as an analyst for the city's 2008 health status report and helped establish a baseline metric for flu reporting. In the state legislature, I was exposed to the complexities legislation, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. I coordinated with these stakeholders to amend legislation, and more importantly digest and subsequently communicate a variety of technical complexities to the delegate.

Education-wise, I'm finishing up a DPhil in Biophysics at the University of Oxford. My thesis entails computational modeling of DNA and single-molecule fluorescence studies of a DNA helicase implicated in rare childhood genetic disorders that greatly increase cancer risk. My undergraduate degree is in Biomedical Engineering and Economics from a leading US biomedical research institution, Johns Hopkins University.

For PRMA, my value added lies not only in the bio and econ fundamentals, but in my ability to reduce ideas to practice, through either data analysis or coordination with key stakeholders.

I have work authorization in the US (indefinite) and UK (1 year through Tier 4 Doctorate Extension Scheme). Thanks for taking the time to review my application.

\vspace{1\baselineskip}
% Closing
Sincerely,
\vspace{2\baselineskip}

Ryan M Harrison \\
DPhil Student, Biophysics\\
University of Oxford \\


\end{resume} 
\end{sloppypar}
\end{document} 



