% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass[a4paper]{../res} 

\include{../preambleResume}
\textwidth=6.5in
\textheight 11.00in %RMH

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
11 May 2014

% Inside address
Jean-Paul Petranca \\
The Boston Consulting Group \\
20 Manchester Square \\
London W1U 3PZ
%\vspace{1\baselineskip}

% Opening
Dear Mr. Petranca,

\textbf{Re: Summer-cycle Junior Consultant via Oxford recruiting, London Office}

The thrill of advising a client by applying insight to data -- it is the reason I want to become a consultant.

Believe it or not, it's also what I do every day as a scientist. A DPhil in Computational Biophysics may sound fancy and unrelated to the business of delivering value to clients; however, this couldn't be further from the truth. At its core, being a scientist is about building relationships with fellow academics, assimilating information to the edge of the known, and synthesizing to make an intuitive leap into the previously unknown.

For example, a few months ago I was contacted by Professor Susanta Sarkar of the Colorado School of Mines. He was writing a grant proposal, and needed help with choosing a labeling locations on a protein, a speciality I'm intimately familiar with having used the technique to propose a mechanism for an unrelated class of proteins. He briefed me on the literature in his field and explained his motivations. I mocked up a prototype of his system, worked out a plausible scheme that could pass muster with grant reviewers, and most importantly, delivered an actionable result.  

The sense of pride you feel when helping someone towards their goals, on problems they may have thought intractable, is reward enough; but, this particular `engagement' was even more meaningful. Professor Sarkar, when he was just Susanta, was my mentor; he taught me everything I know about microscopy.

The decision to pursue a career in consulting is not one I took lightly. The aim is not to abandon my training; rather, to gain a broader perspective and ultimately be more impactfull than I could ever hope as a scientist. Over the years, I've met with BCG at the Oxford Consultancy Fairs, spoken to BCG consultants at your dedicated DPhil networking events and taken on a team-based Oxford Student Consultancy project. I've also reached out to numerous consultants that have transitioned from PhD to consulting, and whom, despite their hectic schedules and abundant obligations, were kind enough to offer advise on the journey.

One of these consultants is BCG Principal Dr. Michael Anstey. Over drinks in his invaluable free-time, he impressed upon me how potent the analytical and problem solving expertise of a doctorate can be when applied through the lens of business, a path I hope to follow. The most lasting insight was that the value of the doctorate isn't in the technical skills, or the coalition building, or the art of freebie gathering, but in the grit it endears. The constant struggle through failure and overcoming self-doubt to deliver a result. Your current client may be difficult, but is nothing compared to the humiliation of being dressed-down by the department chair during your first departmental seminar, tooling up to counter all comers during the second, and embodying your domain during the third.

%I understand that the transformation from PhD to consultant require dedication and sacrifice -- tolls I have borne for causes I believe in, be it delivering potable water to a village in the Guatemalan highlands or helping build the world's first high-throughput organism engineering foundry. Tolls I am more than happy to pay to build business acumen in the best training environment available. I'm committed to beginning my career in consulting and will take the knocks to grow into the role of trusted advisor. 

For BCG, my value added is the ability to reduce ideas to practice, by working with people to bring insight to data. I'm committed to beginning my career in consulting and would relish the opportunity to work with BCG, build business acumen in the best training environment available. Thank you for your time and consideration; I look forward to hearing from you.

%Naturally, I'm excited by the prospect of working with a diverse array of clients. 

%I'm an ideal fit for BCG and would welcome the opportunity to grow with the firm as a junior consultant in the London or Boston offices.

%\vspace{1\baselineskip}
% Closing
Sincerely, \\
Ryan M Harrison \\
DPhil Candidate \\
Computational Biophysics \\
University of Oxford  \\
Work authorization: US Citizen, UK Tier 4 Doctorate Extension Scheme (until Aug 2015)

\end{resume} 
\end{sloppypar}
\end{document} 



