% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass[a4paper]{../res} 
\include{../preambleResume}
\textwidth=6.5in
%\addtolength{\textheight}{-3cm}

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\vspace{1\baselineskip}

% Date
9 November 2013

% Inside address
Holly Johnson \\
Associate Recruitment Coordinator \\
L.E.K. Consulting \\
40 Grosvenor Pl \\
London SW1X 7JL

% Opening
Dear Ms. Johnson,

\textbf{Re: Associate position via Oxford recruiting, London Office}

As a final year DPhil in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills. My thesis entails computational modeling of DNA and single-molecule fluorescence studies of a DNA helicase implicated in rare childhood genetic disorders that greatly increase cancer risk. My undergraduate degree is in Biomedical Engineering and Economics from a leading US biomedical research institution, Johns Hopkins University. The aim is not to abandon my training; rather, to gain a broader perspective and ultimately command considerably more leverage as a consultant, than I ever could in the lab.

I've met with L.E.K. at the Oxford Consultancy Fair, taken on a team-based Oxford Student Consultancy project and reached out to PhD scientists that have successfully made the transition. They have impressed upon me how potent the analytical and problem solving expertise of a doctorate can be when applied through the lens of business, a path I hope to follow. I'm committed to beginning my career in consulting and think that L.E.K. would be a great place to start.

The life sciences practice would be a strong fit, given my life sciences background. While I intend to gain exposure to a diverse array of industries in the first few years; in the longer-term, I would value working with a practice that fully utilizes my doctorate and technical background, including:
\begin{itemize}[itemindent=1cm]
    \item Extensive knowledge of DNA and protein structure
    \item Programming and analytical ability to test my hypothesise on real data
    \item Experience with devices and instrumentation
    \item Practical experience with doctors and patients through work and volunteering in hospital 
\end{itemize}
Why would I disregard these valuable experiences to fit into a consultancy that doesn't value life sciences sector expertise or the value-added of a doctorate. A compelling argument, and one of the reasons I'm so drawn to L.E.K..

Understandably, one may wonder what, other than raw analytical horsepower, a freshly minted DPhil can bring to the firm. One illustrative example of client/stakeholder management in a high-stakes environment is my work as a legislative aide to a Maryland State Legislature delegate, representing 100k constituents. I continued work on his anti-smoking legislation and coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. I was exposed to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. More importantly, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices.

For L.E.K., my value added lies in my ability to reduce ideas to practice, through either data analysis or coordination with key stakeholders. Thank you for your time and look forward to chatting soon.

% Closing
Sincerely, \\
Ryan M Harrison \\
PS. Work authorization: US (indefinite), UK (Aug-2015 via Tier 4 Doctorate Extension Scheme). 


\end{resume} 
\end{sloppypar}
\end{document} 



