% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 
\usepackage{csquotes}

\include{../preambleResume}
\textwidth=6.5in
\addtolength{\textheight}{-3cm}

\textheight 9in %RMH
\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
%\vspace{1\baselineskip}
5 May 2014

% Inside address
Lana Rousom \\
Lake Partners Strategy Consultants, Inc. \\
1000 Second Avenue, Suite 3600 \\
Seattle, Washington 98104

Mrs. Rousom:

\textbf{Re: Analyst/Junior Associate via Johns Hopkins University Recruiting}

% Write the body of the letter
Please consider me for an analyst/junior associate position. I'm an ideal fit for Lake Partners and would welcome the opportunity to reconnect with the firm.

I've been interested in Lake Partners since 2008 when I had the pleasure of interviewing with the firm, while completing a degree in Biomedical Engineering from Johns Hopkins University. Dr. Swaroop Mishra was kind enough to take the time to interview in Georgetown, and you handled my application logistics. 

Five years later, I'm now finishing up a DPhil (PhD) in Biophysics from the University of Oxford, through the support of NSF and NIH fellowships. My interest in strategy consulting has emerged stronger, supported by the expertise and grit a doctorate endears. More importantly, through work experience, both technical and non-technical, I have built confidence and abilities that I lacked as a fresh Uni grad. 

I will be relocating back to the US in August 2014, and Lake Partners is an even better fit now, than it was those many years ago. 

The offer is a strong mutual fit, and a solid value proposition consisting of:
\begin{enumerate}
    \item A highly developed quantitative tool kit manifest from years of engineering training and,
    \item a demonstrated interest in business, supported by volunteering, econometrics and strategy coursework. 
\end{enumerate}


One of things I enjoy most is working in teams to rapidly spin-up on, and solve complex problems. As a doctorate student, I've taken the liberty to do just that, applying my quantitative toolkit in a variety of industries, including in a non-technical policy settings.

One notable example is working as a legislative aide working with the Maryland General Assembly Health Committee, specifically the health disparities and insurance subcommittee. I reworked the logistics backend to deliver mailed session status reports to 6k people, shepherded 3 bills from conception to passage and coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. The process exposed me to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. None of this would have been possible without teamwork, effective communication and wholehearted dedication to the client, in this case the delegate and his constituents. More important than any individual outcome, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices. I suspect these are the types of `soft skills' I'd use every day with Lake Partners.

My motivations for relocating to Seattle haven't changed much in the intervening years, so I'll quote from the original '08 application:

\blockquote{While I'm not from the Seattle area, I would love to relocate. I spent the summer of 2007 in Seattle, working full-time at the University of Washington in the Department of Bioengineering. Seattle is also the birthplace of Rosetta, a protein structure prediction suite spearheaded by the Bakerlab at UW. I served as a developer of for over four years and have presented numerous times at the Rosetta Developers Conference held annually in Leavenworth (with some time spent at Bakerlab). Needless to say, I fell in love with the place; joining up with a friend from Hopkins (Bellevue area) to go hiking just about every weekend -- all the usual suspects: Snow Lake, Mt. Si, Rainer, Mt. Mastiff/Mt. Howard double bagger and of course the Olympics (northern parts around Elwha River, didn't get a chance to hike the Hoh valley).}

I sincerly hope we can grow together. Thank you for your time and consideration.

% Closing
Sincerely, \\
Ryan M Harrison, DPhil Candidate \\
Computational Biophysics \\
University of Oxford \\ \\
Work authorization: US Citizen, UK Tier 4 Doctorate Extension Scheme (until Aug 2015)
\end{resume} 
\end{sloppypar}
\end{document} 



