% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\include{../preambleResume}
\textwidth=6.5in
\addtolength{\textheight}{-3cm}

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
%\vspace{1\baselineskip}
26 April 2014

% Inside address
Dr. Chris Von Seggern \\
ClearView Healthcare Partners \\
One Newton Place \\
275 Washington Street, Suite 405 \\
Newton, MA 02458
%\vspace{1\baselineskip}

% Opening
Dr. Von Seggern:

\textbf{Re: Off-cycle Consultant (parrallel application with Connect to ClearView)}

% Write the body of the letter
I want to become a life sciences consultant with ClearView; however, this letter isn't about me -- please review the Connect to ClearView application for a more personal perspective -- this letter is about you.

%about how I can deliver value for ClearView.
The offer is a strong mutual fit, and a solid value proposition consisting of i) life sciences industry software/wetlab experience and ii) a demonstrated interest in the broader life sciences ecosystem, namely of business and policy, from a budding life sciences consultant intent on relocating to your area in August 2014.

In early 2009 your firm took the time to interview me for an analyst position. I withdrew this application, and have, in the interim, becoming a far stronger candidate with respect to soft skills and technical skill sets. 

An example of non-technical impact is my work as a legislative aide working with the Maryland General Assembly Health Committee, specifically the health disparities and insurance subcommittee. I reworked the logistics backend to deliver mailed session status reports to 6k people, shepherded 3 bills from conception to passage and coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. The process exposed me to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. None of this would have been possible without teamwork, effective communication and wholehearted dedication to the client, in this case the delegate and his constituents. More important than any individual outcome, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices. I suspect these are the types of `soft skills' I'd use every day with ClearView.

On the technical side, I built software and subsequently integrated it with the lab to complete a high-throughput DNA plasmid assembly pipeline for a Boston-based synthetic biology start-up. I gathered requirements and interfaced with all layers of the company. Most importantly, I delivered. The initial software completed a grant milestone worth about 6 months of company funding, and the subsequent integration positioned the firm to compete for larger-scale contracts. In a more recent example, I took my knowledge of molecular simulation, a thesis component, and applied it to a completely different field, procedural character animation. I took the initiative to convey my results in a format that they intutitively understood, building real-time demos of my character animation improvements and iteratively presenting them to sales, designers and animators. Only through communication is the worth of a technical advance realized. I suspect this wholehearted deidcation to delivering on time, above target and in a format the client understands, is an expectation for ClearView consultant.

Thank you for your time and consideration. I'd be happy to further discuss these, and other, examples of client engagement and impact.

% Closing
Sincerely, \\
Ryan M Harrison, DPhil Candidate, Computational Biophysics, University of Oxford \\
Work authorization: US Citizen, UK Tier 4 Doctorate Extension Scheme (until Aug 2015)
\end{resume} 
\end{sloppypar}
\end{document} 



