% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\include{../preambleResume}
\textwidth=6.5in
\addtolength{\textheight}{-3cm}

\textheight 11in %RMH
\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
%\vspace{1\baselineskip}
5 May 2014

% Inside address
Kara Caesar \\
Mars \& Co. \\
124 Mason Street \\
Greenwich, CT 06830 \\ \\
Ms. Caesar:

\textbf{Re: Senior Associate Consultant via Johns Hopkins University Recruiting}

% Write the body of the letter
I want to grow with Mars \& Co because I appreciate the firm's commitment to training, promoting from within, and outright avoiding the conflicts of interest that taint the broader strategy consulting ecosystem. I enjoyed meeting with some of your colleagues at the Oxford careers fairs over the years. 

The offer is a strong mutual fit, and a solid value proposition consisting of: 
i) a highly developed quantitative tool kit manifest from years of engineering training as well as a computational biophysics doctorate, and 
ii) a demonstrated interest in business, supported by volunteering, econometrics and strategy coursework. 

I will be relocating back to the US in August 2014 after completing a doctorate at the University of Oxford under the aegis and generous fellowship support of the US National Science Foundation and National Institutes of Health.

One of things I enjoy most is working in teams to rapidly spin-up on, and solve complex problems. As a doctorate student, I've taken the liberty to do just that, applying my quantitative toolkit in a variety of industries, including in a non-technical policy settings.

One notable example is working as a legislative aide working with the Maryland General Assembly Health Committee, specifically the health disparities and insurance subcommittee. I reworked the logistics backend to deliver mailed session status reports to 6k people, shepherded 3 bills from conception to passage and coordinated closely with stakeholders to the Insurance and Health Disparities subcommittees. The process exposed me to the complexities of the legislative process, revolving around the competing interest of doctors, hospitals, insurers, pharma and device manufacturers. None of this would have been possible without teamwork, effective communication and wholehearted dedication to the client, in this case the delegate and his constituents. More important than any individual outcome, I learned how to manage up, to best provide the delegate with actionable material, as well as laterally, to coordinate with legislative staff in other offices. I suspect these are the types of `soft skills' I'd use every day with Mars.

I do not possess mastery of a foreign language, but as evidenced by earning an advanced degree abroad, a business/economics studying abroad in Denmark, a 3 month research placement in Japan and engineering development work in Central America, I am no stranger to integrating with highly international teams in unfamiliar environs.

I sincerly hope we can grow together. Thank you for your time and consideration.

% Closing
Sincerely, \\
Ryan M Harrison, DPhil Candidate \\
Computational Biophysics \\
University of Oxford \\ \\
Work authorization: US Citizen, UK Tier 4 Doctorate Extension Scheme (until Aug 2015)
\end{resume} 
\end{sloppypar}
\end{document} 



