% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% From http://www.rpi.edu/dept/arc/training/latex/resumes/

\documentclass{../res} 

\include{../preambleResume}
\textwidth=6.5in
\addtolength{\textheight}{-3cm}

\begin{document} 
\begin{sloppypar}
 
%\include{includeHeader}
\include{../headerResume}

\begin{resume} 
%\noindent\rule{5.2in}{0.75pt}
%\setlength{\parskip}{1.00ex}
%\setlength{\parindent}{0pt}
 
% Date
17 March 2014

% Inside address
Attn. James Sietstra \\
Seven Bridges Genomics, Inc. \\
Suite \#208, 625 Mt. Auburn St.  \\
Cambridge, MA 02138
%\vspace{1\baselineskip}

% Opening
Dear Dr. Sietstra:

\textbf{Re: Cambridge -- Enterprise Platform Bioinformatician via Oxford University Recruiting}

% Write the body of the letter
As a final year doctoral candidate in Computational Biophysics at the University of Oxford, I've honed my analytical and quantitative skills through years of training. With Seven Bridges, I want to apply this hard earned skill set to helping clients solve their toughest *omics challenges. 

My technical value to Seven Bridges stems from three core competencies: 
\begin{enumerate}[itemindent=1cm]
    \item Solid biological training, from DNA structure to genomics.
    \item Collaborative software development experience in C++ and Python
    \item Extensive simulation method and data processing experience
\end{enumerate}

These core competencies are backed by both a solid academic foundation and practical industry experience, for example improving read quality at a next-generation sequencing company, building DNA CAD software for a synthetic biology start-up or serving as a developer for two biomolecular modelling software programs.

I am a competent bench scientist and programmer, but what I enjoy most is translating between the technical and non-technical. This is why I'm applying for the Enterprise Platform Bioinformatician position as opposed to Genome Scientist, for which I am also qualified.

One example of this translation was with NaturalMotion, a game middleware company. R\&D wanted someone with simulation experience to work with a newly developed numerical solver for the procedural animation of complex game characters. Having previously worked with small companies, I wanted to learn about Agile development in a more corporate environment. 

Instead of just focusing on the code, I built usable demos to communicate the principles and improvements to 3D artist and game programmers, folks who usually see R\&D as dead weight. To my surprise, the head of sales even took the time to play with a demo. On the technical side, I took the lessons of NaturalMotion back to my research group, where I pushed for a refactor of our analysis toolchain, implemented auto-documentation and built an integration test suite. These tools have improved usability and dramatically reduced the occurrence of bugs. 

I believe the combination of technical acumen and non-technical communication make me a great candidate for the Enterprise Platform Bioinformatician role. Thank you for your time and attention.

% Closing
Sincerely, \\
Ryan M Harrison, DPhil Candidate \\
Computational Biophysics \\
University of Oxford  \\
PS. Relocating to Boston for early Fall 2014 start. \\
Work Authorization: US Citizen, UK Tier 4 Doctorate Extension Scheme.
\end{resume} 
\end{sloppypar}
\end{document} 



